### 2012-06-03 1.tex
Chapter 2 draft done.

\chapter{Sequence structure constraints in generative grammar}
\label{msc}

@@

\citet{Jakobson1932} attributes a number of phonological properites of the Russian imperative to morpheme juncture. The vast majority of Russian infinitives consist of the stem followed by a theme vowel and /t\pal/. The reflexive is marked wih a final /-sə/ which feeds a general process of regressive voicing assimilation. In the reflexive infinitive, /\ldots t\pal-s\ldots/ is realized [ts], with no palatalization. However, palatalization of a stem-final labial or coronal---including /t\pal/, as in (\ref{russian}c)---is preserved in the reflexive imperative.

\begin{example}
\label{russian}
Russian reflexives \citep[after][]{Jakobson1932}:\footnote{I have taken a number of liberties with \citeauthor{Jakobson1932}'s presentation of the data, which uses an abstract phonemic transcription. Thanks to Lev Blumenfeld (p.c.) for help with the transcription of this data.}

\begin{tabular}{l l l l} %\toprule
   &  infinitive      & imperative \\ %\midrule
a. & [slav\pal itsə]  & [slaf\pal s\pal ə]  & `be glorious'    \\
   & [upram\pal itsə] & [upram\pal s\pal ə] & `be stubborn'    \\
b. & [kras\pal itsə]  & [kras\pal s\pal ə]  & `put on makeup'  \\
   & [ʒar\pal itsə]   & [ʒar\pal s\pal ə]   & `roast'          \\
c. & [zəbytsə]        & [zəbut\pal s\pal ə] & `forget' \\ %\bottomrule
%   & ab\'utsa      & ab\'ujsa     & `put on shoes'   \\
\end{tabular}
\end{example}

>>>>

%\chapter{Sequence structure constraints in generative grammar}
\label{msc}

@@

\citet{Jakobson1932} attributes a number of phonological properites of the Russian imperative to morpheme juncture. The vast majority of Russian infinitives consist of the stem followed by a theme vowel and /t\pal/. The reflexive is marked wih a final /-sə/ which feeds a general process of regressive voicing assimilation. In the reflexive infinitive, /\ldots t\pal-s\ldots/ is realized [ts], with no palatalization. However, palatalization of a stem-final labial or coronal---including /t\pal/, as in (\ref{russian}c)---is preserved in the reflexive imperative.\footnote{I have taken a number of liberties with \citeauthor{Jakobson1932}'s presentation of the data, which uses an abstract phonemic transcription. Thanks to Lev Blumenfeld (p.c.) for help with the transcription of this data.}

\begin{example}[Russian reflexives (after \citealt[][]{Jakobson1932}] \label{russian}
\begin{tabular}{l l l l} %\toprule
   &  infinitive      & imperative \\ %\midrule
a. & [slav\pal itsə]  & [slaf\pal s\pal ə]  & `be glorious'    \\
   & [upram\pal itsə] & [upram\pal s\pal ə] & `be stubborn'    \\
b. & [kras\pal itsə]  & [kras\pal s\pal ə]  & `put on makeup'  \\
   & [ʒar\pal itsə]   & [ʒar\pal s\pal ə]   & `roast'          \\
c. & [zəbytsə]        & [zəbut\pal s\pal ə] & `forget' \\ %\bottomrule
%   & ab\'utsa      & ab\'ujsa     & `put on shoes'   \\
\end{tabular}
\end{example}
